---
bibliography: "OUTPUT/packages.bib"
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(magrittr)
```
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/bocinsky/asian_niche/commits/master) 
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
[![DOI](https://zenodo.org/badge/52899692.svg)](https://zenodo.org/badge/latestdoi/52899692)

## Research compendium for d'Alpoim Guedes and Bocinsky *in review*

d'Alpoim Guedes, Jade and R. Kyle Bocinsky. Climate change stimulated agricultural innovation and exchange across Asia. Submitted to *Nature*.

### Compendium DOI: 
 
[![DOI](https://zenodo.org/badge/52899692.svg)](https://zenodo.org/badge/latestdoi/52899692)

The files at the URL above will generate the results as found in the publication. The files hosted at [https://github.com/bocinsky/asian_niche](https://github.com/bocinsky/asian_niche) are the development versions and may have changed since this compendium was released.

### Authors  of this repository:

- R. Kyle Bocinsky ([bocinsky@gmail.com](mailto:bocinsky@gmail.com))
- Jade d'Alpoim Guedes ([jadeguedes@gmail.com](mailto:jadeguedes@gmail.com))

### Overview of contents
This repository is a research compendium for d'Alpoim Guedes and Bocinsky (in review). The compendium contains all code associated with the analyses described and presented in the publication, as well as a Docker environment (described in the `Dockerfile`) for running the code. The primary files contained in this reposity are:

- **`README.Rmd`**: An RMarkdown source file, and its knitted Markdown output `README.md`
- **`asian_niche.Rproj`**: An RStudio project configuration file for this study
- **`asian_niche.R`**: The R script that runs the entire analysis, and is designed to be called from the command prompt
- **`asian_niche.srun`**: The configuration script for the [Slurm Workload Manager](https://slurm.schedmd.com/) that was used to run this analysis on the [Kamiak high performance computing cluster](https://hpc.wsu.edu/) at Washington State University
- **`asian_niche.sh`**: A Bash script for building the Docker container (see below), running `asian_niche.R`, and compressing the output for uploading to Zenodo
- **`Dockerfile`**: A text document that contains the instructions for building the Docker container
- **`LICENSE`**: A text file of the MIT license for this repository and the code within it
- **`src/`**: A directory containing auxiliary R code for functions used in the `asian_niche.R` script
- **`DATA/`**: A directory containing input data for the analysis not downloaded from elsewhere. This includes `crops.csv`, a table of cultivars and their estimated thermal requirements.

### The research compendium
To download this research compendium as you see it on GitHub, for offline browsing, [install git on your computer](https://git-scm.com/) and use this line at the shell prompt:

```bash
git clone https://github.com/bocinsky/asian_niche.git
```

### Archaeological site data
Archaeological site location data is sensitive information due to the possibility of looting, and archaeological ethics require that we restrict access to those data. Accordingly, an essential component of this analysis is **not** shipped in this open GitHub repository or archived with Zenodo. We have instead archived the site location data necessary to run this analysis with the [Digital Archaeological Record (tDAR)](https://www.tdar.org/) under restricted access. Users who want to run this analysis need to request access through tDAR, which we will provide to any researcher with a reasonable affiliation (academic or otherwise). The main purpose is to track to whom we provide access to these data. Please [contact the authors](mailto:bocinsky@gmail.com,jadeguedes@gmail.com) if you wish to share these data or use them in your research.

The data are available through tDAR at the following DOI: [10.6067/XCV8MK6G05](https://doi.org/10.6067/XCV8MK6G05). Please go to the site and select "Request Access, Submit Correction, Comment" under the downloads section in the right panel. You will have to [create a tDAR user account](https://core.tdar.org/account/new) and agree to the [tDAR user agreement](https://www.tdar.org/about/policies/terms-of-use/).

Once you have access, you should be able to download the `DALPOIMGUEDES_BOCINSKY_2017.xlsx` Microsoft Excel file. Place the file in the `asian_niche/DATA/` directory, where you should also find the `crops.csv` file.

### The Docker container
[Docker](https://www.docker.com/) is a virtual computing environment that facilitates reproducible research---it allows for research results to be produced independent of the machine on which they are computed. Docker users describe computing environments in a text format called a "Dockerfile", which when read by the Docker software builds a virtual machine, or "container". Other users can then load the container on their own computers. Users can upload container images to [Docker Hub](https://hub.docker.com/), and the image for this research is available at [https://hub.docker.com/r/bocinsky/asian_niche/](https://hub.docker.com/r/bocinsky/asian_niche/).

We have included a Dockerfile which builds a Docker container for running the analyses described in the paper. It uses [`rocker/geospatial:3.3.3`](https://hub.docker.com/r/rocker/geospatial/), which provides R, [RStudio Server](https://www.rstudio.com/products/rstudio/download-server/), the [tidyverse](http://tidyverse.org/) of R packages as its base image and adds several geospatial software packages ([GDAL](http://www.gdal.org/), [GEOS](https://trac.osgeo.org/geos/), and [proj.4](http://proj4.org/). The Dockerimage (1) adds ffmpeg, (2) updates the R packages to the [2017-05-15 MRAN snapshot](https://mran.microsoft.com/timemachine/), and (3) installs the R software packages required by the script (based on the same MRAN snapshot).

#### Downloading and running the Docker container image
The commands below demonstrate three ways to run the docker container. In each, we use the `-v` argument to mount the local `asian_niche` directory (cloned from GitHub above, or dowloaded from Zenodo) to the running container; we use the `-w` argument to set the working directory to `/asian_niche`; and we use the `--rm` argument to dispose of containers upon exiting. See this [Docker cheat sheet](https://github.com/wsargent/docker-cheat-sheet) for other arguments.

First, set an environment variable to the absolute path of where you cloned this repository, such as:
```bash
export WKDIR=/Users/bocinsky/git/asian_niche/
```

##### Run the analysis directly
To run the analyses directly, call the `asian_niche.R` script at the end of the run command:
```bash
docker run --rm -v $WKDIR:/asian_niche -w /asian_niche bocinsky/asian_niche:1.0.0 Rscript asian_niche.R
```

##### Run the analysis interactively from the terminal
Alternatively, you can run the container in interactive mode and load the script yourself:
```bash
docker run --rm -v $WKDIR:/asian_niche -w /asian_niche -it bocinsky/asian_niche:1.0.0 bash
```
The `asian_niche.R` script has been designed to be run from the terminal using Python-style argument parsing---see an example in the `asian_niche.srun` file. To run, simply enter `Rscript --vanilla asian_niche.R` at the shell prompt. Passing the `--vanilla` option runs the script in a "fresh" R environment. Run `Rscript asian_niche.R --help` to see all available options.

You can use the `exit` command to stop the container.

##### Run the analysis from within a Dockerized RStudio IDE
Finally, you can host RStudio Server locally to use the RStudio browser-based IDE. Run:
```bash
docker run --rm -v $WKDIR:/home/rstudio/asian_niche -p 8787:8787 bocinsky/asian_niche:1.0.0
```
Then, open a browser (we find [Chrome](https://www.google.com/chrome/) works best) and navigate to "localhost:8787" or or run `docker-machine ip default` in the shell to find the correct IP address, and log in with **rstudio**/**rstudio** as the user name and password. In the explorer (lower right pane in RStudio), navigate to the `asian_niche` directory, and click the `asian_niche.Rproj` to open the project.

#### Building the Docker container
If you wish to build the Docker container locally for this project from scratch, simply `cd` into the `asian_niche/` directory and run:

```bash
docker build -t bocinsky/asian_niche:1.0.0 .
```
The `-t` argument gives the resulting container image a name. You can then run the container as described above.

### Output
The GitHub repository for this project does not contain the output generated by the script---`r "OUTPUT" %>% list.files(all.files = TRUE, recursive = TRUE, full.names = TRUE) %>% file.size() %>% sum() %>% magrittr::divide_by(1000000000) %>% round(digits = 2)` GB. All output data is available as a separate Zenodo archive at

<!-- http://dx.doi.org/xxxxxxx -->

The `OUTPUT/` directory contains all data generated by the `asian_niche.R` script:

- `session_info.txt` describes the computational infrastructure within which the script was run
- `DATA/` contains data downloaded from web sources for this analysis   
- `MODELS/` contains R data objects describing the Kriging interpolation models across the study area
- `RECONS/` contains NetCDF format raster bricks of the model output (i.e., the reconstructed crop niches)
- `SITE_DENSITIES/` contains figures of the estimated chronometric probability density for each site in our database
- `FIGURES/` contains all figures output by the script, including videos of how each crop niche changes over time
- `TABLES/` contains tables of the raw site chronometric data without locational information, and the modeled chronometric probability and niche information for each site.

### Licenses

Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: R. Kyle Bocinsky and Jade d'Alpoim Guedes

### Contact

Kyle Bocinsky\\
Research Associate\\
Crow Canyon Archaeological Center\\
23390 Road K, Cortez, CO  81321\\
970.564.4384 – Office\\
770.362.6659 – Mobile\\
[bocinsky@gmail.com](mailto:bocinsky@gmail.com) – Email\\
[bocinsky.io](http://www.bocinsky.io/) – Web\\

### R package citation
The following R packages were used for this analysis:
```{r, echo = FALSE, message = FALSE}
library("knitcitations")
knitcitations::cleanbib()

knitcitations::read.bibtex(out("packages.bib")) %>%
  knitcitations::record_as_cited()

knitcitations::write.bibtex(file = out("packages.bib"))

package_citations <- knitcitations::read.bibtex(out("packages.bib")) %>% names()
```
---
nocite: | 
  `r paste0("@",package_citations) %>% paste0(collapse = ", ")`
...


